---
title: "Report title"
subtitle: "Short descriptive subtitle"
author:
  - name: Analyst Name
    affiliations:
      - name: Neudata Consulting Ltd
date: today
date-format: "D MMMM YYYY"
client: "Client organisation"
reference: "NDC-2026-000"
confidentiality: "Confidential"
abstract: |
  One-paragraph executive summary: the question, the data, the approach and the
  headline finding. Keep it readable by a non-technical decision-maker.
format:
  neudata-html: default
  neudata-typst: default
  neudata-docx: default
---

```{r}
#| label: setup
library(ggplot2)

neudata_cols <- c("#055F56", "#0B376C", "#04242F", "#5FA39B", "#6C8DB8", "#8A99A3")

theme_set(
  theme_minimal(base_size = 11) +
    theme(
      plot.title = element_text(face = "bold", colour = "#04242F"),
      axis.title = element_text(colour = "#04242F"),
      panel.grid.minor = element_blank(),
      legend.position = "bottom"
    )
)
```

# Introduction

Describe the background, the client's objective and the questions this report answers.

::: {.key-findings}
**Key findings**

- Finding one, stated plainly with its size and uncertainty.
- Finding two.
- Recommendation or implication for the client.
:::

# Data and methods

Summarise the data sources, inclusion criteria, variables and statistical methods. Refer to the statistical analysis plan for full detail.

# Results

## Descriptive summary

@tbl-summary summarises the example data.

```{r}
#| label: tbl-summary
#| tbl-cap: "Mean tooth length by supplement and dose (example data)."
summary_tbl <- aggregate(len ~ supp + dose, data = ToothGrowth, FUN = function(x) round(mean(x), 1))
names(summary_tbl) <- c("Supplement", "Dose (mg/day)", "Mean length")
knitr::kable(summary_tbl)
```

## Main analysis

@fig-main shows the relationship using the Neudata palette.

```{r}
#| label: fig-main
#| fig-cap: "Tooth length by dose and supplement (example data)."
#| fig-width: 7
#| fig-height: 4
ggplot(ToothGrowth, aes(factor(dose), len, fill = supp)) +
  geom_boxplot(alpha = 0.85, outlier.shape = NA) +
  geom_jitter(aes(colour = supp), width = 0.15, size = 1.2, alpha = 0.7, show.legend = FALSE) +
  scale_fill_manual(values = neudata_cols, name = "Supplement") +
  scale_colour_manual(values = neudata_cols) +
  labs(x = "Dose (mg/day)", y = "Tooth length")
```

# Discussion

Interpret the results, note limitations and set out recommendations.

::: {.callout-note}
## Reproducibility

This report was generated from code. Software versions are listed in the appendix.
:::

# Appendix {.appendix}

```{r}
#| label: session
#| echo: true
sessionInfo()$R.version$version.string
```
